Hydra Battles and Cie

### 2021-09-13 doc/JFLA2022/paper.tex
small corrections

Our proof is very different from the computational proof of Fig\ref{fig:Ex42E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$ to get the equality we want to prove.

@@

\inputsnippets{Schutte/Ex42c, Schutte/Ex42d, Schutte/Ex42e}

>>>>

Our proof is very different from the computational proof of Fig\ref{fig:Ex42E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$ to  fprove our lemma.

@@

\inputsnippets{Schutte/Ex42d, Schutte/Ex42c, Schutte/Ex42e}

### 2021-09-13 doc/part-hydras.tex
minor changes
draft paper
small changes
small corrections

The proof is very different from the computational proof of Sect~\vref{Ex42-E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$ to get the equality we want to prove.

@@

\input{movies/snippets/Schutte/Ex42d}

>>>>

Our proof is very different from the computational proof of Sect~\vref{Ex42-E0}.
By definition of additive principal ordinals, 
it suffices to prove the inequality $\omega+42< \phi_0(2)$.

@@

\inputsnippets{Schutte/Ex42d, Schutte/Ex42c,  Schutte/Ex42e}
